---
title: "Richness by combined zones"
abstract: |
  This is the abstract.
output: 
  html_document:
    code_folding: hide
    toc: true
date: "`r format(Sys.time(), '%d %B %Y')`"
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      fig.align = 'center',
                      fig.height=8, 
                      fig.width=7, 
                      message=FALSE, 
                      warning=FALSE, 
                      cache=TRUE)

```

This notebook uses species richness layers created by SDM and polygons for three landscape variables to compare species richness distributions within the zones created by the three variables.  

The landscape variables/polygons are natural protected areas (ANPs), the 7 ecoregiones (aka. biomes) of Mexico, and landcover classified into vegetation, agriculture, and other. The ANP variable considers inside protected areas, within 10 km of the areas, and greater than 10 km from a protected area. These zone polygons were previously created (prep_create_zone_polygons.R).

The richness layers were created by stacking species distribution models (SDMs) that were produced for every species considered (process_SDM_v2.R). 

The result of the notebook is a collection of graphics displaying richness for each zone and indicating whether the differences in richness are statistically significant.

```{r initialize, message=FALSE}
# Load libraries and initialize variables
source('R/initialize.R')
library(rcompanion)

samp_n <- 350
# sessionInfo()

# Directory paths
dat_dir <- here::here('data', 'data_out')

# Zones raster and lookup table
zone_polys_dir <- file.path('data', 'tidy', 'analysis_zones', 'from_v1')
zones_fn <- 'v1_stack_anps3_biomes7_usv3'
zones_ras_fp <- file.path(zone_polys_dir, str_c(zones_fn, '.tif'))
zones_lu_fp <- file.path(zone_polys_dir, str_c(zones_fn, '_lu.rds'))

# Zones raster and lookup table
zone_polys_dir <- file.path('data', 'tidy', 'analysis_zones')
zones_fn <- 'stack_anp_biome_3x7'
zones_ras_fp <- file.path(zone_polys_dir, str_c(zones_fn, '.tif'))
zones_lu_fp <- file.path(zone_polys_dir, str_c(zones_fn, '_lu.rds'))

# Directory for richness dataframes
div_dir <- file.path(pred_dir, 'diversity_by_zones', zones_fn)
dir.create(div_dir, recursive=TRUE, showWarnings = F)
```

Parameters:

* unq_cells: **`r unq_cells`**
* excludep: **`r excludep`**
* filt_dates: **`r }filt_dates`**
* buffer_distance: **`r buffer_distance` km**

### Pre-process ANP, biome, and land use zones

```{r pre-process, eval=TRUE}
if(!file.exists(zones_ras_fp)){
  
  # Input pollinator richness 
  fps <- list.files(file.path(pred_dir, 'richness'), '*\\.tif', full.names = TRUE)
  rich_ras <- terra::rast(fps[[1]])
      
  # Rasterize ANP zones
  anps <- rasterize_zones(anp_zones_fp, rich_ras, 
                              field = 'zone', overwrite = TRUE)
  
  # Rasterize ecoregions
  biom <- rasterize_zones(biom_diss_fp, rich_ras, 
                              field = 'DESECON1', overwrite = TRUE)

  # Rasterize landcover
  # usv_fn <- 'usv250s6gw_diss_3class.gpkg'
  # usv_fp <- file.path(zone_polys_dir, usv_fn)
  # biom <- rasterize_zones(biom_diss_fp, rich_ras, 
  #                             field = 'DESECON1', overwrite = TRUE)

  # Combine zone rasters
  combo_ras <- c(anps$r, biom$r)
  names(combo_ras) <- c('anp_zone', 'biome')
  
  combo_ras %>% terra::writeRaster(zones_ras_fp, overwrite=T)
  
  # Save lookup tables
  saveRDS( list(anp = anps$lu, biom = biom$lu), file=zones_lu_fp)
} 
```

### Richness data frames

Convert rasters to dataframes of richness by ANP zone, biome, land cover, and pollinator group. 

```{r make div_df}
# Load stacked zones
combo_ras <- terra::rast(zones_ras_fp)

# List richness tifs
(fps <- list.files(file.path(pred_dir, 'richness'),
                       '*\\.tif', full.names = TRUE))

extract_stats_to_csv <- function(rich_tif_fp){
  
  # Resulting path for CSV
  rich_fn <- basename(tools::file_path_sans_ext(rich_tif_fp))
  pol_group <- str_extract(rich_fn, 'bee|butterfly|moth|hummingbird|bat|wasp|fly')
  div_df_fp <- file.path(div_dir, str_c(rich_fn, '.csv'))
  
  if(!file.exists(div_df_fp)){
    
    # Load raster and add to SpatRaster
    rich_ras <- terra::rast(rich_tif_fp)
    names(rich_ras) <- 'richness'
    combo_all <- c(combo_ras, rich_ras)
    
    # Convert to DF and recode
    div_df <- terra::as.data.frame(combo_all, cells=TRUE) %>% 
      mutate(pol_group = pol_group)
    
    # Save
    div_df %>% write_csv(div_df_fp)
   
  } else {
    div_df <- read_csv(div_df_fp, col_types='ifffdf')
  }
  
  return(div_df) 
}

# Create/load DFs
div_df1 <- fps %>% purrr::map_dfr(extract_stats_to_csv)
```

Combine pollinator richness dataframes into one dataframe with all pollinators.

```{r}
# Recode biome names
lu <- readRDS(zones_lu_fp)
biom_codes_all <- tibble(id = names(lu$biom), name = lu$biom, 
       code=c('CalMedit', 'Desierto', 'ElevSemiar', 'GranPlanic', 
              'SelvCalHum', 'SelvCalSec', 'SierTemp'))
biom_codes <- setNames(biom_codes_all$code, biom_codes_all$id)

# Convert numeric code to factors
div_df <- div_df1 %>% 
      mutate(anp_zone = recode(anp_zone, !!!lu$anp) %>% 
               factor(levels = c('Outside buffer', 'Buffer 10 km', 'Inside NPA')),
             biome = recode(biome, !!!biom_codes) %>% 
               factor(),
             usv = recode(usv, !!!lu$usv) %>% 
               factor(levels = c('veg', 'ag', 'otro')))
```

### Compare richness by zones - ANP zones

The function `get_grp_diffs` evaluates the statistical significance of groups and returns medians, CIs, and significant groups for plotting. It will be applied to each group of pollinator, biome, and either ANP zone or land cover type.

```{r get_grp_diffs}
get_grp_diffs <- function(df, grp_var){
  
  # Get medians and confidence intervals
  f <- str_c('richness ~ ', grp_var)
  Sum <- do.call("groupwiseMedian", 
          list(as.formula(f), 
               data = as.name('df'),
               conf       = 0.95,
                R          = 5000,
                percentile = TRUE,
                bca        = FALSE,
                digits     = 3))
  
  if(length(unique(df[[grp_var]])) == 1) {
    
    print('Only one group.')
    cld <- tibble(zone = unique(df[[grp_var]]), sig_group = 'a')
    
  } else {
    
    # Check whether any groups are significantly different
    kw <- kruskal.test(df[['richness']] ~ df[[grp_var]]) 
    if(kw$p.value > 0.05) print('No significantly different groups')
    
    # Post-hoc test to compare groups
    PT <- pairwise.wilcox.test(df[['richness']], df[[grp_var]], 
                               p.adjust.method = 'fdr')
    PT1 = rcompanion::fullPTable(PT$p.value)
    cld_list <- multcompView::multcompLetters(PT1,
                  compare="<",
                  threshold=0.05,  # p-value to use as significance threshold
                  Letters=letters,
                  reversed = FALSE)
    lv <- cld_list$Letters
    cld <- tibble(sig_group = factor(lv, levels = sort(unique(lv))), 
                  zone = factor(names(lv)))
  
  }

  # Join letter indicating significantly different groups to medians and CIs
  sum1 <- select(tibble(cld), zone, sig_group) %>% 
    left_join(tibble(Sum), 
              by=c(zone=grp_var))
  
  return(sum1)
}

iterate_get_grp_diffs <- function(df_samp, grp_var, var2, grp_diffs_fp, overwrite=FALSE) {
    # Get group differences for each combination of biome and ANP zone
    
    if(file.exists(grp_diffs_fp) & !overwrite) return(readRDS(grp_diffs_fp))
  
    # Nest df by groups
    df_nest <- df_samp %>% 
      group_by(pol_group, biome, .data[[var2]]) %>% 
      nest()
    
    # Run get_grp_diffs for each group
    sum2 <- df_nest %>%
      mutate(sum = purrr::map(data, get_grp_diffs, grp_var)) %>%
      select(-data) %>% 
      unnest(cols=sum)
    
    # significant group factor levels
    sg_levels <- sort(as.character(unique(sum2$sig_group)))
    sum2 <- sum2 %>% 
      mutate(sig_group = factor(sig_group, levels = sg_levels))
    
    # Save 
    sum2 %>% saveRDS(grp_diffs_fp)
    return(sum2)
}
```

```{r plot_pollin_facet, echo=F}
plot_pollin_facet <- function(df, pol_grp, var2='usv', grp_var='anp_zone', 
                              patch.position='inner', legend_on=FALSE){
  
  xmax <- max(df$Percentile.upper)
  
  df_rect <- distinct(df, biome, .data[[var2]], pol_group)
  if(grp_var == 'anp_zone'){
    
    var_levels <- c( 'Outside buffer', 'Buffer 10 km', 'Inside NPA')
    facet_y <- 'Land cover'
    
  } else if (grp_var == 'usv') {
    
    var_levels <- c( 'otro', 'ag', 'veg')
    facet_y <- 'ANP zone'
    
  }
  
  if(var2 != 'pol_group'){
     p <- ggplot(df) +
       
      # shade facet by ANP zone
      geom_rect(data=df_rect, aes(xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = Inf,
                    fill=.data[[var2]]), alpha=0.25, color='white') +
      scale_fill_grey(name = facet_y, start=0.05, end=0.75) 
     
  } else {
    
    p <- ggplot(df)
    
  }
  
  p <- p +
  
    # plot CIs
    geom_errorbar(aes(y = zone, x = Median, color=sig_group,
                      xmin = Percentile.lower, xmax = Percentile.upper),
                   width = 0.3, size  = 0.5) +
    
    # plot medians
     geom_point(aes(y = zone, x = Median, color=sig_group), 
                shape = 15, size  = 2) +
     xlab("Median richness with 95% CI") +
    
    scale_color_manual(values=c('a'='#F8766D', 'ab'='#C77CFF', 'b'='#00BFC4', 
                       'bc'='#7CAE00', 'c'='#DE8C00'), 
                       # limits = c('a', 'ab', 'b', 'bc', 'c'),
                       name='Group',
                       drop=FALSE) +
      
    scale_y_discrete(limits = var_levels) +
    scale_x_continuous(n.breaks= 3) +
  
    # Facet by x=pollinator group, y = ANP zone
    facet_grid(vars(.data[[var2]]), vars(biome)) +
    ggtitle(pol_grp) +
    theme_minimal() +
    theme(
      plot.title = element_text(size=rel(1), face='bold', hjust=0),
      panel.spacing = unit(0.5, 'mm'),
      panel.border=element_blank(),
      # panel.grid = element_line(color='darkgray'), 
      # panel.grid.minor.x = element_line(color='darkgray'),
      panel.grid.major.y=element_blank(),
      panel.ontop = FALSE,
      panel.background = element_blank(),
      axis.title.x = element_blank(),
      axis.title.y = element_blank(), 
      axis.ticks.y = element_blank(),
      # axis.text.x = element_text(margin = margin(t = .2, unit = "mm")),
      strip.text = element_blank(),
      strip.background = element_blank(),
      strip.switch.pad.grid = unit(0.5, 'mm'),
      legend.position = 'none'
      )
  
  return(p)
  
}
```

#### Sample DF

Create stratified random sample of pollinator richness values. `r samp_n` pixels are sampled from each unique combination ecoregion, land cover type, and ANP zone. The same pixels are sampled for each pollinator group, i.e. each pollinator richness layer.

```{r sample-df}
# Stratified random sample
fn_prefix <- fn <- str_c('samp', samp_n, '_rf', rf_vers, 
                         '_', length(levels(div_df$pol_group)), 'pols')
fn <- str_c(fn_prefix, '.rds')
samp_fp <- file.path(div_dir, fn)

if(!file.exists(samp_fp)){
  # Sample the same cells for all the pollinator groups
  
  # Get all usable cells
  samp_idx <- div_df %>% 
    filter(pol_group == 'bee') %>% 
    group_by(anp_zone, biome, usv) %>%
    filter(n() > samp_n)
  
  # Random sample stratified by group
  set.seed(1)
  samp_idx <- samp_idx %>% 
    do(slice_sample(., n=samp_n)) %>%
    ungroup
  
  df_samp <- div_df %>% filter(cell %in% samp_idx$cell)
  
  # Save
  df_samp %>% saveRDS(samp_fp)
  
} else {
  
  df_samp <- readRDS(samp_fp)
  
}
```

### Compare groups
#### Compare by land cover type

```{r compare-usv-x-anp}
grp_var <- 'usv'
var2 <- 'anp_zone'
var2_code <- 'ANPzone'

# File name
fn <- str_c('grpdiffs_', fn_prefix, '_', var2_code, '_', grp_var, '.rds')
grp_diffs_fp <- file.path(div_dir, fn)
sum2 <- iterate_get_grp_diffs(df_samp, grp_var, var2, grp_diffs_fp, overwrite=FALSE)
```

```{r plot-usv-x-anp, fig.width=7, fig.height=8, cache=T}
pol_groups <- levels(sum2$pol_group)

# Plot
p1 <- sum2 %>% filter(pol_group == pol_groups[1]) %>% 
  plot_pollin_facet(pol_groups[1], var2=var2, grp_var=grp_var) +
  theme(strip.text.x = element_text(size=rel(0.8)),
        plot.title = element_text(vjust=0),
        axis.title.x = element_blank())
p2 <- sum2 %>% filter(pol_group == pol_groups[2]) %>% 
  plot_pollin_facet(pol_groups[2], var2=var2, grp_var=grp_var) +
  theme(legend.position = 'right',
        axis.title.x = element_blank())
p3 <- sum2 %>% filter(pol_group == pol_groups[3]) %>% 
  plot_pollin_facet(pol_groups[3], var2=var2, grp_var=grp_var) +
  theme(axis.title.x = element_blank())

# Vary the plotting based on whether we're looking at 3 or 4 groups
if(length(pol_groups) == 4) {
  
  p4 <- sum2 %>% filter(pol_group == pol_groups[4]) %>% 
    plot_pollin_facet(pol_groups[4], var2=var2, grp_var=grp_var) +
    theme(axis.text.x = element_text(margin = margin(t = .2, unit = "mm"),
                                   hjust = c(0, 0.5, 1)
                                   # using a vector here may be deprecated. 
                                   # Alternatives: ggtext + element_markdown()? 
                                   ),
          axis.title.x = element_text())

  plots <- list(p1, p2, p3, p4)
} else {
  p3 <- p3 + theme(
    axis.text.x = element_text(margin = margin(t = .2, unit = "mm"),
                                   hjust = c(0, 0.5, 1) ),
    axis.title.x = element_text())
  
  plots <- list(p1, p2, p3)

}

# Put the plots together
wrap_plots(plots, ncol=1, guides = 'collect') +
  plot_annotation(
    caption = "Different colors within one facet indicate statistically significant (p < 0.05) difference between groups.") & 
  scale_x_continuous(n.breaks=3,
                     limits = c(0, 10)) &
  theme(plot.title.position = 'plot')

# Save figure
fig_fp <- str_c(tools::file_path_sans_ext(grp_diffs_fp), '.png')
if(!file.exists(fig_fp)) ggsave(fig_fp, height=8)

# Plot just one
p1 <- sum2 %>% 
  filter(pol_group == 'bee') %>% 
  plot_pollin_facet('Bees', var2=var2, grp_var=grp_var) +
  theme(strip.text.x = element_text(size=rel(0.8)),
        plot.title = element_text(vjust=0),
        axis.text.x = element_text(margin = margin(t = .2, unit = "mm"),
                                   hjust = c(0, 0.5, 1) ),
        axis.title.x = element_text()) +
  plot_annotation(
    caption = "Different colors within one facet indicate statistically significant (p < 0.05) difference between groups.") & 
  # scale_x_continuous(n.breaks=3,
  #                    limits = c(0, 10)) &
  theme(plot.title.position = 'plot')

# Save figure
fig_fp <- str_c(tools::file_path_sans_ext(grp_diffs_fp), '_bees.png')
if(!file.exists(fig_fp)) ggsave(fig_fp, height=3)
```

#### Compare by ANP zone

```{r compare-anp-x-usv}
grp_var <- 'anp_zone'
grp_var_code <- 'ANPzone'
var2 <- 'usv'

# File name
fn <- str_c('grpdiffs_', fn_prefix, '_', var2, '_', grp_var_code, '.rds')
grp_diffs_fp <- file.path(div_dir, fn)
sum2 <- iterate_get_grp_diffs(df_samp, grp_var, var2, grp_diffs_fp, overwrite=FALSE)
```

```{r plot-anp-x-usv, fig.height=8, fig.width=7, cache=TRUE}
pol_groups <- levels(sum2$pol_group)

# Plot
p1 <- sum2 %>% filter(pol_group == pol_groups[1]) %>% 
  plot_pollin_facet(pol_groups[1], var2=var2, grp_var=grp_var) +
  theme(strip.text.x = element_text(size=rel(0.8)),
        plot.title = element_text(vjust=0),
        axis.text.x = element_blank())
p2 <- sum2 %>% filter(pol_group == pol_groups[2]) %>% 
  plot_pollin_facet(pol_groups[2], var2=var2, grp_var=grp_var) +
  theme(legend.position = 'right',
        axis.text.x = element_blank())
p3 <- sum2 %>% filter(pol_group == pol_groups[3]) %>% 
  plot_pollin_facet(pol_groups[3], var2=var2, grp_var=grp_var) +
  theme(axis.text.x = element_blank())

# Vary the plotting based on whether we're looking at 3 or 4 groups
if(length(pol_groups) == 3){
  p3 <- p3 + theme(
    axis.text.x = element_text(margin = margin(t = .2, unit = "mm"),
                                   hjust = c(0, 0.5, 1) ))
  
  plots <- list(p1, p2, p3)
  
} else if(length(pol_groups) == 4) {
  
  p4 <- sum2 %>% filter(pol_group == pol_groups[4]) %>% 
    plot_pollin_facet(pol_groups[4], var2=var2, grp_var=grp_var) +
    theme(axis.text.x = element_text(margin = margin(t = .2, unit = "mm"),
                                   hjust = c(0, 0.5, 1) ))

  plots <- list(p1, p2, p3, p4)
}

# Put the plots together
wrap_plots(plots, ncol=1, 
           guides = 'collect') +
  plot_annotation(
    caption = "Different colors within one facet indicate statistically significant (p < 0.05) difference between groups.") & 
  scale_x_continuous(n.breaks=3,
                     limits = c(0, 10)) &
  theme(plot.title.position = 'plot')

# Save figure
fig_dir <- here::here('figures', 'diversity_by_zones')
fig_fp <- file.path(fig_dir, dfilt_code,
                    str_c('grpdiffs_samp', samp_n, '_', 
                          grp_var, '_',  rich_code, '_',
                          dfilt_code, '_', nspecies, 'species_',
                          length(levels(div_df$pol_group)), 'pols.png'))
if(!file.exists(fig_fp)) ggsave(fig_fp, height=8)
```

#### Compare by ANP zone without land cover

```{r compare-anp, fig.width=7, fig.height=4, cache=T}
grp_var <- 'anp_zone'
grp_var_code <- 'ANPzone'
var2 <- NA
var2_code <- 'noUSV'

# File name
fn <- str_c('grpdiffs_', fn_prefix, '_', var2_code, '_', grp_var_code, '.rds')
grp_diffs_fp <- file.path(div_dir, fn)

if(!file.exists(grp_diffs_fp)){
  
  # Get group differences for each combination of biome and ANP zone
  if(is.na(var2)){
    df_nest <- df_samp %>% group_by(pol_group, biome) %>% nest()
  } else {
    df_nest <- df_samp %>% group_by(pol_group, biome, .data[[var2]]) %>% nest()
  }
  medians_anp <- df_nest %>%
    mutate(sum = purrr::map(data, get_grp_diffs, grp_var)) %>%
    select(-data) %>% 
    unnest(cols=sum)
  
  sg_levels <- sort(as.character(unique(medians_anp$sig_group)))
  medians_anp <- medians_anp %>% mutate(sig_group = factor(sig_group, 
                                              levels = sg_levels))
  
  # Save 
  medians_anp %>% saveRDS(grp_diffs_fp)
  
} else {
  
  medians_anp <- readRDS(grp_diffs_fp)
  
}

# Plot
medians_anp %>% 
  plot_pollin_facet('All', var2='pol_group', grp_var=grp_var) +
    scale_x_continuous(n.breaks= 4) +
    theme(axis.title.y = element_blank(),
        axis.title.x = element_text(margin= margin(t=6, unit='pt')),
        axis.text.x = element_text(hjust=c(0, 0.5, 1)), 
        plot.title = element_blank(), 
        legend.position = 'bottom', 
        legend.box.spacing = unit(1, 'pt'),
        strip.text = element_text(size=rel(0.8)),
        panel.background = element_rect(fill=alpha('#A6A6A6', 0.3), 
                                        color='white'),
        panel.grid = element_line(color='lightgray'),
        panel.grid.minor.x = element_line(color='lightgray')
        ) +
    labs(caption = "Different colors within one facet indicate statistically significant (p < 0.05) difference between groups.")

# Save figure
fig_fp <- str_c(tools::file_path_sans_ext(grp_diffs_fp), '.png')
if(!file.exists(fig_fp)) ggsave(fig_fp, width=9, height=4)


# Plot only bees
medians_anp %>% 
  filter(pol_group == 'bee') %>% 
  plot_pollin_facet('All', var2='pol_group', grp_var=grp_var) +
    scale_x_continuous(n.breaks= 4) +
    theme(axis.title.y = element_blank(),
        axis.title.x = element_text(margin= margin(t=6, unit='pt')),
        axis.text.x = element_text(hjust=c(0, 0.5, 1)), 
        plot.title = element_blank(), 
        legend.position = 'bottom', 
        legend.box.spacing = unit(1, 'pt'),
        strip.text = element_text(size=rel(0.8)),
        panel.background = element_rect(fill=alpha('#A6A6A6', 0.3), 
                                        color='white'),
        panel.grid = element_line(color='lightgray'),
        panel.grid.minor.x = element_line(color='lightgray')
        ) +
    labs(caption = "Different colors within one facet indicate statistically significant (p < 0.05) difference between groups.")

# Save figure
fig_fp <- str_c(tools::file_path_sans_ext(grp_diffs_fp), '_bees.png')
if(!file.exists(fig_fp)) ggsave(fig_fp, width=9, height=3)
```

#### Compare by land cover without ANP zone

```{r compare-usv, fig.height=4, fig.width=7, warning=FALSE, cache=TRUE}
grp_var <- 'usv'
var2 <- NA

# File name
fn <- str_c('grpdiffs_samp', samp_n, '_', 
            grp_var, '_', 'noANP_',
            rich_code, '_', 
            dfilt_code, '_', nspecies, 'species_',
            length(levels(div_df$pol_group)), 'pols.rds')
grp_diffs_fp <- file.path(div_dir, fn)

if(!file.exists(grp_diffs_fp)){
  
  # Get group differences for each combination of biome and ANP zone
  if(is.na(var2)){
    df_nest <- df_samp %>% group_by(pol_group, biome) %>% nest()
  } else {
    df_nest <- df_samp %>% group_by(pol_group, biome, .data[[var2]]) %>% nest()
  }
  
  # compare richness distribution within groups
  medians_usv <- df_nest %>%
    mutate(sum = purrr::map(data, get_grp_diffs, grp_var)) %>%
    select(-data) %>% 
    unnest(cols=sum)
  
  # establish order for letters (significant groups)
  sg_levels <- sort(as.character(unique(medians_usv$sig_group)))
  medians_usv <- medians_usv %>% mutate(sig_group = factor(sig_group, 
                                              levels = sg_levels))
  
  # Save 
  medians_usv %>% saveRDS(grp_diffs_fp)
  
} else {
  
  medians_usv <- readRDS(grp_diffs_fp)
  
}

# Plot
medians_usv %>% 
  plot_pollin_facet('All', var2='pol_group', grp_var=grp_var) +
    scale_x_continuous(n.breaks= 4) +
    theme(axis.title.y = element_blank(),
        axis.title.x = element_text(margin= margin(t=6, unit='pt')),
        axis.text.x = element_text(hjust=c(0, 0.5, 1)), 
        plot.title = element_blank(), 
        legend.position = 'bottom', 
        legend.box.spacing = unit(1, 'pt'),
        strip.text = element_text(size=rel(0.8)),
        panel.background = element_rect(fill=alpha('#A6A6A6', 0.3), 
                                        color='white'),
        panel.grid = element_line(color='lightgray'),
        panel.grid.minor.x = element_line(color='lightgray')
        ) +
    labs(caption = "Different colors within one facet indicate statistically significant (p < 0.05) difference between groups.")

# Save figure
fig_dir <- here::here('figures', 'diversity_by_zones')
fig_fp <- file.path(fig_dir, dfilt_code,
                    str_c('grpdiffs_samp', samp_n, '_', 
                          grp_var, '_', 'noANP_',
                          rich_code, '_', 
                          dfilt_code, '_', 
                          nspecies, 'species_',
                          length(levels(div_df$pol_group)), 'pols.png'))
if(!file.exists(fig_fp)) ggsave(fig_fp, width=9, height=4)
```











#### Exploratory Plots

```{r, eval=FALSE}
# Plot all groups with facets by biome and pollinators
div_df %>%
  filter(pol_group == 'Colibries', biome== 'Selvas Calido-Secas') %>%
  ggplot(., aes(y=richness, color=usv, fill=usv, x=anp_zone)) +
  geom_boxplot(outlier.size=1, 
                 outlier.alpha = 0.5,
                 # fill=NA, 
               alpha=0.5,
                 width = .85, 
                 notch=T,
                 position = position_dodge2(width = 0.85, preserve="single")) +
  scale_color_viridis_d(option='D', end=0.75, direction=-1,
                        aesthetics = c('color', 'fill'), 
                        "Uso de suelo") +
  theme(legend.position = 'bottom') +
  labs(x=NULL, y='Richness') +
  facet_grid(vars(pol_group), vars(biome))

# Plot richness by ANP zone, faceted by biome
div_df %>%
  ggplot(., aes(y=richness, color=anp_zone, fill=anp_zone, x=anp_zone)) +
  geom_boxplot(outlier.size=1, outlier.alpha = 0.5,
               alpha=0.5,
                 notch=T,
                 width = .85, 
                 position = position_dodge2(width = 0.85, preserve="single")) +
  scale_color_viridis_d(option='D', end=0.75, direction=-1,
                        aesthetics = c('color', 'fill')) +
  theme(legend.position = 'none') +
  labs(x=NULL) +
  facet_wrap(facets=vars(biome))
```

#### Check for significant differences in groups

```{r compare abejas, eval=FALSE}
abejas_df <- div_df %>% filter(pol_group == 'Abejas')
m <- lm(richness ~ anp_zone, data = abejas_df)
g <- multcomp::glht(m, linfct = multcomp::mcp(anp_zone = "Tukey"))
summary(g, test = multcomp::adjusted("holm"))
# 
# abejas_df %>% 
#   ggplot(., aes(x=richness, fill=zone, y=zone)) +
#   geom_boxplot() +
#   theme(legend.position = 'none')  +
#   labs(y=NULL) 

# Kruskal-Wallis test
kruskal.test(richness ~ anp_zone, data = abejas_df) 
kruskal.test(richness ~ biome, data = abejas_df) 
kruskal.test(richness ~ usv, data = abejas_df) 

# Stratified random sample
df_samp <- abejas_df %>%
  filter(biome=='Selvas Calido-Secas', usv=='veg') %>% 
  group_by(anp_zone) %>% 
  do(sample_n(., 20000))
df_samp <- abejas_df %>%
  group_by(anp_zone, biome, usv) %>% 
  do(sample_n(., 64))
kruskal.test(richness ~ anp_zone, data = df_samp) 

# Effect size stats
# 
rcompanion::epsilonSquared(x=df_samp$richness, g=df_samp$anp_zone)
# Freeman's theta == 1 means all values in group are greater (or less) than all values in other group. 0 means groups are stochastically equal. 
rcompanion::freemanTheta(x=df_samp$richness, g=df_samp$anp_zone)
# Vargha and Delaney's A (VDA): probability that an observation from one group is greater than an observation from the other group. Use maximum for overall.
rcompanion::multiVDA(x=df_samp$richness, g=df_samp$anp_zone)

# Post-hoc test
# Dunn test
(DT = FSA::dunnTest(richness ~ anp_zone, data = df_samp, method='bh'))
PT = DT$res
cld <- rcompanion::cldList(P.adj ~ Comparison,
        data = PT,
        threshold = 0.05)

# Plot medians and confidence intervals
Sum = rcompanion::groupwiseMedian(richness ~ anp_zone,
                      data       = df_samp,
                      conf       = 0.95,
                      R          = 5000,
                      percentile = TRUE,
                      bca        = FALSE,
                      digits     = 3)
sum1 <- tibble(Sum) %>% 
  mutate(temp_zone = str_remove_all(anp_zone, ' |0')) %>% 
  left_join(select(tibble(cld), zone, sig_group), by=c(temp_zone='zone'))

ggplot(sum1, aes(x = anp_zone, y = Median, color=sig_group)) +
   geom_errorbar(aes(ymin = Percentile.lower, ymax = Percentile.upper),
                 width = 0.05, size  = 0.5) +
   geom_point(shape = 15, size  = 4) +
   ylab("Median richness with 95% CI")
```
